---
title: "hw8"
author: "Due: 11:59pm Saturday 8/6/2016.  Instructors stop answering questions at 5pm."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
library(dplyr)
library(ggplot2)
library(purrr)
```

### purrr

In this exercise, you'll be using functional programming ideas to simulate the central limit theorem on coin flips.  Using neither loops nor the apply functions, write a simulation pipeline that:

* Generates 1000 samples of each 1, 2, ..., 99, 100 fair coin flips.  So for example, you would simulate flipping 1 coins 1000 times, 2 coins 1000 times, etc.
* For each of the 1, 2, ..., 100 flips, produces a histogram of the proportion of heads.  To be explicit: you will create a histogram for the 1000 proportions calculated from the 1 coin flips.  Then you'll do the same for 2 coin flips, 3, etc.

In your plots
* The x-axis should be limited to 0-1
* The y-axis should be limited to 0-15


```{r, eval = FALSE}
CoinFlip <- function(n) {
  heads <- sample(c(0, 1), size = n, replace = TRUE, prob = c(0.5, 0.5))
  return(sum(heads == 1) / n)
}
samples <- 1000 %>% 
  rerun(map(1:100, CoinFlip)) %>% 
  transpose()

graph <- function(n) {
  data <- unlist(samples[[n]]) %>% data.frame()
  return(ggplot(data) +
           geom_histogram(aes(x = ., y = ..density..)) +
           scale_y_continuous(limits = c(0, 15)))
}

map(1:100 , graph)
```

Now that you have all the static images, you could "animate" the progression by turning the sequence of images into a gif.  This can be achieved with the `animation` package in R or the standalone `ImageMagick` utility.  This is just an FYI, we will not be looking for a GIF.  Also, Please do NOT upload the images to GitHub nor bCourses.  We'll just be checking your code.

## SQL

These exercises are meant to help you wrap your head around SQL.  Answer the questions below using SQL queries.  You can check your answer using `dplyr` methods, but your grade will be based on the SQL commands.  The `nycflights13` data set has been put into a SQLlite database for these problems.  For documentation about the variable names, see

```{r, eval = FALSE}
help(package = "nycflights13")
```

```{r}
flights <- src_sqlite("nycflights13.mysqlite3")
```


1. Find the full name of each airline that flew to Dallas Fort-Worth (DFW).
```{r}
dfw <- flights %>% tbl(sql("
  SELECT DISTINCT
    b.name
  FROM
    nyflights a INNER JOIN nyairlines b
    ON a.carrier = b.carrier
  WHERE
    dest GLOB 'DFW'
")) %>% collect()
```

2. Make a table containing the tail number, year of manufacture, model, number of engines, and number of seats of the planes flown by United Airlines (UA).  Sort the results by year manufactured.

```{r}
ua <- flights %>% tbl(sql("
  SELECT DISTINCT
    b.tailnum, 
    b.year,
    b.model,
    b.engines, 
    b.seats
  FROM
    nyflights a INNER JOIN nyplanes b
    ON a.tailnum = b.tailnum
  WHERE
    a.carrier GLOB 'UA'
  ORDER BY
    b.year ASC,
    b.seats ASC
")) %>% collect()
```

3. Make a table with the following information: full airport name in a column called `Airport` and number of flights from New York City to those airports in 2013 in a column called `NumberOfFlights`.  Sort the results in descending order by flight counts.
```{r}
flight_counts <- flights %>% tbl(sql("
  SELECT
    b.name AS Airport,
    COUNT(flight) AS NumberOfFlights
  FROM
    nyflights a INNER JOIN nyairports b
    ON a.dest = b.faa
  GROUP BY
    AIRPORT
  ORDER BY
    NumberOfFlights DESC
")) %>% collect()
```

4. Find the wind speed during the hour of the sceduled departure time of every flight that had a departure delay of more than 30 minutes.  For example, if a flight was scheduled to leave at 5:59am, you would check the wind speed for 5:00am.  In practice, you would of course be more careful than this.
```{r}
wind_speed <- flights %>% tbl(sql("
  SELECT
    b.wind_speed, a.hour, b.time_hour
  FROM
    nyflights a INNER JOIN nyweather b
    ON a.origin = b.origin AND a.time_hour = b.time_hour
  WHERE
    a.dep_delay > 30
"))
```