---
title: "lab25"
date: "July 26, 2016"
output: html_document
---

Write a function called `moveCars()` that moves the system one full step; that is, the function should move the red cars east once and the blue cars north once, with red cars going first.

Your function should take the following inputs:
`m`: a matrix

Your function should return a list containing two elements:
`m`: an updated matrix
`not_gridlocked`: a logical value that should be TRUE if the system changed and FALSE if not

```{r}
moveCars <- function(m) {
  not_gridlocked <- FALSE
  moved <- FALSE
  for (i in 1:nrow(m)) {
    for (j in 1:ncol(m)) {
      if (!moved) {
        if (m[i,j] == 1 & j != ncol(m)) {
          if (m[i,j+1] == 0) {
            m[i,j+1] = 1
            m[i,j] = 0
            moved <- TRUE
          }
        } else if (m[i,j] == 1 & j == ncol(m) & m[i,1] == 0) {
            m[i,1] = 1
            m[i,ncol(m)] = 0
        } else if (m[i,j] == 2 & i != 1) {
          if (m[i-1,j] == 0) {
            m[i-1,j] = 2
            m[i,j] = 0
          }
        } else if (m[i,j] == 2 & i == 1) {
            if (m[nrow(m),j] == 0) {
              m[nrow(m),j] = 2
              m[i,j] = 0
            }
        }
        not_gridlocked <- TRUE
      } else {
        moved <- FALSE
      }
    }
  }
  return(list(m, not_gridlocked))
}
```


Check:
```{r}
m <- matrix(c(1,0,0,0,2,1,2,0,0,2,0,1,1,0,1,2,0,1,2,1,0,0,1,1,2), nrow = 5, ncol = 5, byrow = T)
identical(moveCars(m), list(matrix(c(0,1,0,0,2,1,2,0,0,2,1,1,0,1,0,2,0,1,2,1,0,0,1,1,2), nrow = 5, ncol = 5, byrow = T), TRUE))

m <-  matrix(c(0,1,0,2,1), nrow = 1, ncol = 5, byrow = T)
identical(moveCars(m), list(matrix(c(1,0,1,2,0), nrow = 1, ncol = 5, byrow = T), TRUE))

m <- matrix(c(2,0,1,2,0), nrow = 5, ncol = 1, byrow = T)
identical(moveCars(m), list(matrix(c(0,0,1,2,2), nrow = 5, ncol = 1, byrow = T), TRUE))
```

Now write a function called `initGrid()` that randomizes the initial system.

Your function should take the following inputs:
`r`: number of rows in the matrix
`c`: number of columns in the matrix
`d`: density of the grid 

Your function should return the following:
`m`: an rxc matrix with entries 0 (no cars), 1 (red cars), or 2 (blue cars)

```{r}
initGrid <- function(r, c, d) {
  m <- matrix(0, nrow = r, ncol = c)
  m <- apply(m, c(1,2), function(x) ifelse(
    sample(c(TRUE, FALSE), 1, prob = c(d, 1-d)), 
    x <- sample(c(1,2), 1), x <- 0))
  return(m)
}
```






