---
title: "lab4"
author: "Andrew Do"
date: "June 13, 2016"
output: html_document
---

```{r setup, include=FALSE}
library(stringr)
library(readr)
knitr::opts_chunk$set(echo = TRUE)
```

## Getting Help for Packages

You can see what an entire package has to offer with
```{r}
help(package = "stringr")
```


## Counting number of vowels

Consider the following vector `letrs` which contains various letters:
```{r}
# Garbage string
letrs <- "gfngenodgsyctyviqyyigeinyngbkwjdjqkrrollhpxdkfldlytympmcgmjynihusebtq"
```

If you were to count the number of vowels in `letrs` you would get the following counts:

- a: 0
- e: 3
- i: 4
- o: 2
- u: 1

This exercise will guide you through how to arrive at this frequency table.

```{r}
# Create a character vector of vowels.  Give it an appropriate name.
vowels <- c('a', 'e', 'i', 'o', 'u')

# Use str_count to get the counts.  Assign this an appropriate name.
vowel_count <- str_count(letrs, vowels)

# Give each element of the vector a name using the names function.
# The result should look like:
# a e i o u
# 0 3 4 2 1
names(vowel_count) <- vowels
vowel_count
```

## Exploring new functions: str_pad
Write a short description of what each of the following calls of `str_pad` is doing.  The last three examples were found at the bottom of the function's documentation.

1. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", width = 4, side = "left", pad = "x")
```
This pads the string "a" with 3 "x"s to the left so that the width of the new string is now 4.

2. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", width = 3, side = "left")
```
This pads the string "a" with 2 spaces to the left so that the width of the new string is now 3.

3. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad(c("a", "abc", "abcdef"), 10)
```
This pads each string in the vector with spaces to the left so that each is width 10.

4. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", c(5, 10, 20))
```
This creates a vector of strings, padding the string "a" with spaces to the left so it is width 5, 10, and 20. 

5. In this call of `str_pad`, __YOUR DESCRIPTION__.
```{r}
str_pad("a", 10, pad = c("-", "_", " "))
```
This creates a vector of strings, each width 10 and adds - to the first string, _ to the second, and spaces to the third all to the left of "a",

## Regular Expressions

We read in the data from the csv file and extract the names column
```{r}
flags <- read_csv("flags.csv")
countries <- flags$name
```

You may have noticed that in the `countries` vector, words in a country's name are separated by `-`.  Use `str_replace_all` to replace the hyphens with spaces.  For example `"Vatican-City"` should be replaced with `"Vatican City"`

```{r}
# Your code here
str_replace_all(countries, "-", " ")
```

Use `str_detect` to see if there are any countries with the world "island" in them, ignoring case.  You may also want to look up how to use `ignore.case`.

```{r}
# Your code here
any(str_detect(countries, ignore.case("island")))
```

Use `str_subset` to find all countries that begin with a capital `A`.
```{r}
# Your code here
str_subset(countries, "^A")
```

Find all countries that end with `stan`
```{r}
# Your code here
str_subset(countries, "stan$")
```

Use `str_replace_all` to replace the `$`'s in `baws` with `s`'s.  Recall that the `$` is a metacharacter.
```{r}
baws <- "Bo$$"
str_replace_all(baws, "\\$", "s")
```

Use a character class (denoted by square brackets) to find all countries beginning with a vowel and ending with a consonant.
```{r}
# Fill in
str_subset(countries, "^[AEIOU].+[^aeiouAEIOU]$")
```